Why do languages tolerate heterography? An experimental investigation into the emergence of informative orthography

### 2023-11-02 manuscript/manuscript.tex
Final manuscript version before submission

% PREPRINT VERSION
\authorsnames{Jon W. Carr, Kathleen Rastle}

\authorsaffiliations{{Department of Psychology, Royal Holloway, University of London, England}}

\authornote{\textbf{Cite as:} Carr, J.\@ W., \& Rastle, K.\@ (2023). Why do languages tolerate heterography? An experimental investigation into the emergence of informative orthography. \textit{OSF Preprints}. Version~1. https://doi.org/10.31219/osf.io/r5n3g}

% SUBMISSION VERSION
% \authorsnames{Anonymous}

% \authorsaffiliations{{Anonymous}}

@@

\keywords{communication; cultural evolution; informativity; iterated learning; language evolution; orthography; spelling; sound change; writing}

@@

\textcite{Kirby:2008} described the first experimental application of the iterated learning framework (which had previously been confined to computational modeling), showing that compositional structure---a systematic relationship between recombinant linguistic units and meaning---could spontaneously emerge under a \textit{bottleneck on transmission}. This ``bottleneck'' defines a limit on the amount of information that can flow from one generation to the next \parencite{Brighton:2002}. Under a tight bottleneck, where little data passes from one generation to the next, the learner must perform more generalization from less input, such that the cognitive biases that the learner brings to the table become more important in shaping the structure of the emergent language. Generalization from limited input is a big driver behind systematic structure in the language as a whole, since human learners tend to generalize in ways that increase the simplicity (i.e., systematicity) of the system, albeit unconsciously \parencite{Culbertson:2016}. However, left unchecked, this bias for simplicity would ultimately result in the emergence of maximally simple, degenerate languages. \textcite{Kirby:2015} therefore extended the framework by including a communicative task; instead of each generation consisting of a single participant, each generation now consisted of a pair of participants engaged in a shared task requiring communicative precision. Crucially, this communicative component prevented the artificial languages from degenerating; instead, the languages find a tradeoff between simplicity on the one hand and informativeness on the other, just as in natural language \parencite{Mollica:2021, KempRegier:2012, Kemp:2018, Regier:2015, Zaslavsky:2018}. We follow this experimental approach in order to compare what happens to orthography when a pressure for informativeness \textit{is} and \textit{is~not} present. [KATHY: I feel that someone could wrongly think that we're just replicating what's already been done but with spelling.  Is there a way to remind readers here that we're looking at what pressures a spelling system to diverge from spoken language?  the key in our experiment is that diverging from spoken language increases pressure on learning.]

@@

Our first experiment tests the ability of the differentiation model to explain the emergence of informativeness in orthography [KATHY: Possible to remind readers that we mean divergence from spoken language i.e. making the orthography more complex?] (i.e., in the face of homophony). We had two main hypotheses:
\begin{enumerate}
	\item Under pressure from learning alone, we expect to see the emergence of an increasingly transparent orthography.
	\item Under additional pressure for disambiguation, we expect to see greater use of differentiated, non-transparent spellings.
\end{enumerate}

@@

To evaluate this argument statistically, we fit the following regression model:
	\begin{equation}
	\begin{aligned}
	   c_i & \sim \mathrm{Normal}(\mu_i, \sigma) \\
	 \mu_i & =    \alpha + \beta_1 g_i + \beta_2 g_i^2 + \beta_3 g_i^3 \\
	\sigma & \sim \mathrm{Exponential}(1),
	\end{aligned}
	\end{equation}
where $g$ is a centered generation number (i.e., Generations~1 through 9 are represented as~$-4$ through $+4$). The model states that the cost~$c$ of participant~$i$'s output system is drawn from a normal distribution, the mean of which is determined by a third-degree polynomial model. The intercept $\alpha$ corresponds to Generation~5 (the central generation), and the $\beta$ parameters determine the shape of the polynomial. $\sigma$ represents an across-participant noise term and is given a regularizing exponential prior. The priors on $\alpha$ and $\beta$ are not shown here, for brevity, but these parameters are estimated separately for each chain and pooled into global estimates with the use of Normal hyperpriors. For the complete model specification, see the Supplementary Material.

@@

To evaluate statistically the effect of generation on cost across the two conditions, while also taking epoch into account, we fit the following regression model:
	\begin{equation}
	\begin{aligned}
	   c_i & \sim \mathrm{Normal}(\mu_i, \sigma) \\
	 \mu_i & =    \alpha_{\mathrm{EPOCH}[i]} + \beta_{\mathrm{EPOCH}[i]} g_i \\
	\sigma & \sim \mathrm{Exponential}(1),
	\end{aligned}
	\end{equation}
where $g$ is an epoch-centered generation number (i.e., for Generations~1, 4, and~7, $g=-1$, for Generations~2, 5, and~8, $g=0$, and for Generations~3, 6, and~9, $g=1$). Overall, the model states that the cost~$c$ of participant~$i$'s output system is drawn from a normal distribution, the mean of which is determined by an epoch-specific linear model (i.e., each epoch has an independent intercept $\alpha$ and slope $\beta$). $\sigma$ represents an across-participant noise term and is given a regularizing exponential prior. The priors on $\alpha$ and $\beta$ are not shown here, for brevity, but these parameters are estimated separately for each chain and pooled into global estimates with the use of Normal hyperpriors. For the complete model specification, see the Supplementary Material.

@@

[JON: something about the cultural ratchet. with each successive sound change, new heterography appears, but once it's present, it's hard to let go of it. Thus, the informativeness of the writing system ratchets up with successive sound changes.]

Our findings did indeed show that informative heterography may be conserved more frequently and for longer periods under communicative pressure for disambiguation. There are two important caveats, however. First, we found that cultural transmission alone---that is, blind learning and reproduction---will result in at~least some conservation, not only in form but also in the conditioning of form on meaning. Cases such as Chain~D correspond to the ``accident of history'' explanation: Expressive orthography is preserved not because it serves any useful purpose (recall that in Transmission-only there is no functional need for the language to be informative), but because participants are simply reproducing what they learned, and what they learned has not (yet) placed a significant enough burden on learning for simplification to kick~in. The additional level of conservation that occurs in Transmission~+ Communication corresponds to the exaptation/repurposing explanation; that is, expressive orthography that originally served one purpose (representing speech) is maintained for a new purpose (representing meaning directly). The second caveat is that, in the long term, it appears that transparency will ultimately win the day, even under communicative pressure. Chain~O, for example, went from expressive to degenerate in two generations under full homophony pressure, and it seems likely [KATHY: on what basis?] that all chains will ultimately undergo the same transformation eventually. Informative heterography that arises through conservation is but a temporary oasis on the march toward transparency.

@@

These conclusions must be interpreted within the limitations of these experiments, which are, after all, highly simplified simulacra of real-world processes. Besides the general scaling-down of orthography, phonology, morphology, and semantics to an experimentally tractable test case, one notable issue we faced was how to induce pressure for informativeness in the written modality. We follow a large body of recent studies by using a real-time communication game \parencite[e.g.,][]{Carr:2017, Kanwal:2017, Kirby:2015, Raviv:2018, Saldana:2019, Silvey:2019, Winters:2015}, but such games are not very representative of the dynamics involved in asynchronous written communication \parencite[although see][for some approaches]{Winters:2019}. That being said, much written communication in the present day is indeed synchronous (e.g., text messaging), potentially allowing the dynamics typically associated with synchronous communication, such as repair, stress, and emotion, to play a role in the development of written forms of the language \parencite{Lupyan:2016}.

@@

\noindent This work was funded by a Leverhulme Trust Research Project Grant (grant number: RPG-2020-034) awarded to K.R.

@@

\section{Appendix}

\subsection{Experiment 1 regression model}

@@

\subsection{Experiment 2 regression model}

@@

\begin{table}
\begin{center}
\begin{threeparttable}
\caption{Experiment 1 posterior parameter estimates}
\footnotesize
\begin{tabular}{lrrrrrr}
\toprule
 & Mean & SD & HDI (5\%) & HDI (95\%) & ESS & $\hat{R}$ \\
\midrule
\multicolumn{7}{c}{Transmission-only} \\
$\alpha_\mu$    &  1.298 &  0.123 &   1.098 &    1.498 &   55213 &    1.0 \\
$\beta_{1_\mu}$ &  0.003 &  0.030 &  -0.048 &    0.051 &   19478 &    1.0 \\
$\beta_{2_\mu}$ & -0.021 &  0.008 &  -0.034 &   -0.009 &   49158 &    1.0 \\
$\beta_{3_\mu}$ &  0.007 &  0.002 &   0.004 &    0.010 &   13927 &    1.0 \\
$\sigma$        &  0.192 &  0.020 &   0.160 &    0.225 &   26492 &    1.0 \\
\midrule
\multicolumn{7}{c}{Transmission + Communication} \\
$\alpha_\mu$    &  0.985 &  0.079 &   0.854 &    1.112 &   22089 &    1.0 \\
$\beta_{1_\mu}$ &  0.003 &  0.059 &  -0.091 &    0.100 &   19115 &    1.0 \\
$\beta_{2_\mu}$ & -0.017 &  0.007 &  -0.030 &   -0.005 &   15955 &    1.0 \\
$\beta_{3_\mu}$ &  0.004 &  0.004 &  -0.002 &    0.010 &   12773 &    1.0 \\
$\sigma$        &  0.370 &  0.034 &   0.313 &    0.425 &   27848 &    1.0 \\
\midrule
\multicolumn{7}{c}{Difference} \\
$\Delta(\alpha_\mu)$    & -0.313 &  0.147 &  -0.551 &   -0.072 &   38539 &    1.0 \\
$\Delta(\beta_{1_\mu})$ & -0.000 &  0.066 &  -0.109 &    0.107 &   19664 &    1.0 \\
$\Delta(\beta_{2_\mu})$ &  0.004 &  0.011 &  -0.014 &    0.022 &   24478 &    1.0 \\
$\Delta(\beta_{3_\mu})$ & -0.003 &  0.004 &  -0.010 &    0.003 &   12532 &    1.0 \\
$\Delta(\sigma)$        &  0.178 &  0.040 &   0.112 &    0.242 &   28446 &    1.0 \\
\bottomrule
\end{tabular}
\label{exp1_parameter_estimates}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{threeparttable}
\caption{Experiment 2 posterior parameter estimates}
\footnotesize
\begin{tabular}{lrrrrrr}
\toprule
 &   Mean &     SD &  HDI (5\%) &  HDI (95\%) &  ESS &  $\hat{R}$ \\
\midrule
\multicolumn{7}{c}{Transmission-only} \\
$\alpha_{1_\mu}$ &  0.099 &  0.066 &  -0.009 & 0.205 &   50911 &    1.0 \\
$\alpha_{2_\mu}$ &  0.530 &  0.134 &   0.320 & 0.748 &   58969 &    1.0 \\
$\alpha_{3_\mu}$ &  1.113 &  0.155 &   0.869 & 1.370 &   55884 &    1.0 \\
$\beta_{1_\mu}$  &  0.048 &  0.044 &  -0.021 & 0.121 &   32489 &    1.0 \\
$\beta_{2_\mu}$  &  0.216 &  0.074 &   0.096 & 0.336 &   47941 &    1.0 \\
$\beta_{3_\mu}$  & -0.000 &  0.040 &  -0.065 & 0.065 &   32801 &    1.0 \\
$\sigma$         &  0.145 &  0.018 &   0.116 & 0.173 &   15490 &    1.0 \\
\midrule
\multicolumn{7}{c}{Transmission + Communication} \\
$\alpha_{1_\mu}$ &  0.052 &  0.042 &  -0.018 & 0.118 &   30904 &    1.0 \\
$\alpha_{2_\mu}$ &  0.297 &  0.102 &   0.138 & 0.469 &   56334 &    1.0 \\
$\alpha_{3_\mu}$ &  0.679 &  0.184 &   0.386 & 0.981 &   63206 &    1.0 \\
$\beta_{1_\mu}$  &  0.033 &  0.044 &  -0.040 & 0.102 &   18241 &    1.0 \\
$\beta_{2_\mu}$  &  0.093 &  0.073 &  -0.027 & 0.209 &   39754 &    1.0 \\
$\beta_{3_\mu}$  &  0.167 &  0.121 &  -0.033 & 0.359 &   53767 &    1.0 \\
$\sigma$         &  0.175 &  0.020 &   0.141 & 0.207 &   17902 &    1.0 \\
\midrule
\multicolumn{7}{c}{Difference} \\
$\Delta(\alpha_{1_\mu})$ & -0.047 &  0.079 &  -0.178 &    0.077 &   40911 &    1.0 \\
$\Delta(\alpha_{2_\mu})$ & -0.233 &  0.168 &  -0.504 &    0.040 &   55907 &    1.0 \\
$\Delta(\alpha_{3_\mu})$ & -0.434 &  0.241 &  -0.825 &   -0.037 &   57860 &    1.0 \\
$\Delta(\beta_{1_\mu})$  & -0.016 &  0.062 &  -0.118 &    0.084 &   23610 &    1.0 \\
$\Delta(\beta_{2_\mu})$  & -0.124 &  0.105 &  -0.295 &    0.047 &   35386 &    1.0 \\
$\Delta(\beta_{3_\mu})$  &  0.167 &  0.128 &  -0.045 &    0.371 &   50705 &    1.0 \\
$\Delta(σ)$              &  0.030 &  0.027 &  -0.014 &    0.074 &   16452 &    1.0 \\
\bottomrule
\end{tabular}
\label{exp2_parameter_estimates}
\end{threeparttable}
\end{center}
\end{table}

>>>>

\authorsnames{Anonymous}

\authorsaffiliations{{Anonymous}}

@@

\keywords{communication; iterated learning; language evolution; orthography; reading; writing}

@@

\textcite{Kirby:2008} described the first experimental application of the iterated learning framework (which had previously been confined to computational modeling), showing that compositional structure---a systematic relationship between recombinant linguistic units and meaning---could spontaneously emerge under a \textit{bottleneck on transmission}. This ``bottleneck'' defines a limit on the amount of information that can flow from one generation to the next \parencite{Brighton:2002}. Under a tight bottleneck, where little data passes from one generation to the next, the learner must perform more generalization from less input, such that the cognitive biases that the learner brings to the table become more important in shaping the structure of the emergent language. Generalization from limited input is a major driver of systematic structure in the language as a whole, since human learners tend to generalize in ways that increase the simplicity (i.e., systematicity) of the system, albeit unconsciously \parencite{Culbertson:2016}. However, left unchecked, this bias for simplicity would ultimately result in the emergence of maximally simple, degenerate languages. \textcite{Kirby:2015} therefore extended the framework by including a communicative task; instead of each generation consisting of a single participant, each generation now consisted of a pair of participants engaged in a shared task requiring communicative precision. Crucially, this communicative component prevented the artificial languages from degenerating; instead, the languages find a tradeoff between simplicity on the one hand and informativeness on the other, just as in natural language \parencite{Mollica:2021, KempRegier:2012, Kemp:2018, Regier:2015, Zaslavsky:2018}.

@@

Our first experiment tests the ability of the differentiation model to explain the emergence of informative orthography. Can variant spellings become conditioned on meaning, such that the written form of the language diverges from the spoken form in a way that is expressive, despite the extra cost in learning? We had two main hypotheses:
\begin{enumerate}
	\item Under pressure from learning alone, we expect to see the emergence of an increasingly transparent orthography.
	\item Under additional pressure for disambiguation, we expect to see greater use of differentiated, non-transparent spellings.
\end{enumerate}

@@

To evaluate this argument statistically, we fit the following regression model:
	\begin{equation}
	\begin{aligned}
	   c_i & \sim \mathrm{Normal}(\mu_i, \sigma) \\
	 \mu_i & =    \alpha + \beta_1 g_i + \beta_2 g_i^2 + \beta_3 g_i^3 \\
	\sigma & \sim \mathrm{Exponential}(1),
	\end{aligned}
	\end{equation}
where $g$ is a centered generation number (i.e., Generations~1 through 9 are represented as~$-4$ through $+4$). The model states that the cost~$c$ of participant~$i$'s output system is drawn from a normal distribution, the mean of which is determined by a third-degree polynomial model. The intercept $\alpha$ corresponds to Generation~5 (the central generation), and the $\beta$ parameters determine the shape of the polynomial. $\sigma$ represents an across-participant noise term and is given a regularizing exponential prior. The priors on $\alpha$ and $\beta$ are not shown here, for brevity, but these parameters are estimated separately for each chain and pooled into global estimates with the use of Normal hyperpriors. For the complete model specification, see Appendix~A.

@@

To evaluate statistically the effect of generation on cost across the two conditions, while also taking epoch into account, we fit the following regression model:
	\begin{equation}
	\begin{aligned}
	   c_i & \sim \mathrm{Normal}(\mu_i, \sigma) \\
	 \mu_i & =    \alpha_{\mathrm{EPOCH}[i]} + \beta_{\mathrm{EPOCH}[i]} g_i \\
	\sigma & \sim \mathrm{Exponential}(1),
	\end{aligned}
	\end{equation}
where $g$ is an epoch-centered generation number (i.e., for Generations~1, 4, and~7, $g=-1$, for Generations~2, 5, and~8, $g=0$, and for Generations~3, 6, and~9, $g=1$). Overall, the model states that the cost~$c$ of participant~$i$'s output system is drawn from a normal distribution, the mean of which is determined by an epoch-specific linear model (i.e., each epoch has an independent intercept $\alpha$ and slope $\beta$). $\sigma$ represents an across-participant noise term and is given a regularizing exponential prior. The priors on $\alpha$ and $\beta$ are not shown here, for brevity, but these parameters are estimated separately for each chain and pooled into global estimates with the use of Normal hyperpriors. For the complete model specification, see Appendix~B.

@@

Our findings did indeed show that informative heterography may be conserved more frequently and for longer periods under communicative pressure for disambiguation. There are two important caveats, however. First, we found that cultural transmission alone---that is, blind learning and reproduction---will result in at~least some conservation, not only in form but also in the conditioning of form on meaning. Cases such as Chain~D correspond to the ``accident of history'' explanation: Expressive orthography is preserved not because it serves any useful purpose (recall that in Transmission-only there is no functional need for the language to be informative), but because participants are simply reproducing what they learned, and what they learned has not (yet) placed a significant enough burden on learning for simplification to kick~in. The additional level of conservation that occurs in Transmission~+ Communication corresponds to the repurposing explanation; that is, expressive orthography that originally served one purpose (representing speech) is maintained for a new purpose (representing meaning directly). The second caveat is that, in the long term, it appears that transparency will ultimately win the day, even under communicative pressure. Chain~O, for example, went from expressive to degenerate in two generations under full homophony pressure, and based on the trajectories of the communicative cost curves (Fig.~\ref{cost_con}), it seems likely that all chains will ultimately undergo the same transformation eventually. Informative heterography that arises through conservation is but a temporary oasis on the march toward transparency.

@@

These conclusions must be interpreted within the limitations of these experiments, which are, after all, highly simplified simulacra of real-world processes. Besides the general scaling-down of orthography, phonology, morphology, and semantics to an experimentally tractable test case, one notable issue we faced was how to induce pressure for informativeness in the written modality. We follow a large body of recent studies by using a real-time communication game \parencite[e.g.,][]{Carr:2017, Kanwal:2017, Kirby:2015, Raviv:2018, Saldana:2019, Silvey:2019, Winters:2015}, but such games are not very representative of the dynamics involved in asynchronous written communication \parencite[although see][for some approaches]{Winters:2019}. That being said, much written communication in the present day is indeed synchronous (e.g., text messaging), potentially allowing the dynamics typically associated with synchronous communication, such as repair, to play a role in the development of written forms of the language \parencite{Lupyan:2016}.

@@

\noindent This work was funded by a Leverhulme Trust Research Project Grant (grant number: RPG-2020-034).

@@

\appendix

\section{}

@@

\begin{table}[h]
\begin{center}
\begin{threeparttable}
\caption{Experiment 1 posterior parameter estimates}
\footnotesize
\begin{tabular}{lrrrrrr}
\toprule
 & Mean & SD & HDI (5\%) & HDI (95\%) & ESS & $\hat{R}$ \\
\midrule
\multicolumn{7}{c}{Transmission-only} \\
$\alpha_\mu$    &  1.298 &  0.123 &   1.098 &    1.498 &   55213 &    1.0 \\
$\beta_{1_\mu}$ &  0.003 &  0.030 &  -0.048 &    0.051 &   19478 &    1.0 \\
$\beta_{2_\mu}$ & -0.021 &  0.008 &  -0.034 &   -0.009 &   49158 &    1.0 \\
$\beta_{3_\mu}$ &  0.007 &  0.002 &   0.004 &    0.010 &   13927 &    1.0 \\
$\sigma$        &  0.192 &  0.020 &   0.160 &    0.225 &   26492 &    1.0 \\
\midrule
\multicolumn{7}{c}{Transmission + Communication} \\
$\alpha_\mu$    &  0.985 &  0.079 &   0.854 &    1.112 &   22089 &    1.0 \\
$\beta_{1_\mu}$ &  0.003 &  0.059 &  -0.091 &    0.100 &   19115 &    1.0 \\
$\beta_{2_\mu}$ & -0.017 &  0.007 &  -0.030 &   -0.005 &   15955 &    1.0 \\
$\beta_{3_\mu}$ &  0.004 &  0.004 &  -0.002 &    0.010 &   12773 &    1.0 \\
$\sigma$        &  0.370 &  0.034 &   0.313 &    0.425 &   27848 &    1.0 \\
\midrule
\multicolumn{7}{c}{Difference} \\
$\Delta(\alpha_\mu)$    & -0.313 &  0.147 &  -0.551 &   -0.072 &   38539 &    1.0 \\
$\Delta(\beta_{1_\mu})$ & -0.000 &  0.066 &  -0.109 &    0.107 &   19664 &    1.0 \\
$\Delta(\beta_{2_\mu})$ &  0.004 &  0.011 &  -0.014 &    0.022 &   24478 &    1.0 \\
$\Delta(\beta_{3_\mu})$ & -0.003 &  0.004 &  -0.010 &    0.003 &   12532 &    1.0 \\
$\Delta(\sigma)$        &  0.178 &  0.040 &   0.112 &    0.242 &   28446 &    1.0 \\
\bottomrule
\end{tabular}
\label{exp1_parameter_estimates}
\end{threeparttable}
\end{center}
\end{table}

\section{}

@@

\begin{table}[h]
\begin{center}
\begin{threeparttable}
\caption{Experiment 2 posterior parameter estimates}
\footnotesize
\begin{tabular}{lrrrrrr}
\toprule
 &   Mean &     SD &  HDI (5\%) &  HDI (95\%) &  ESS &  $\hat{R}$ \\
\midrule
\multicolumn{7}{c}{Transmission-only} \\
$\alpha_{1_\mu}$ &  0.099 &  0.066 &  -0.009 & 0.205 &   50911 &    1.0 \\
$\alpha_{2_\mu}$ &  0.530 &  0.134 &   0.320 & 0.748 &   58969 &    1.0 \\
$\alpha_{3_\mu}$ &  1.113 &  0.155 &   0.869 & 1.370 &   55884 &    1.0 \\
$\beta_{1_\mu}$  &  0.048 &  0.044 &  -0.021 & 0.121 &   32489 &    1.0 \\
$\beta_{2_\mu}$  &  0.216 &  0.074 &   0.096 & 0.336 &   47941 &    1.0 \\
$\beta_{3_\mu}$  & -0.000 &  0.040 &  -0.065 & 0.065 &   32801 &    1.0 \\
$\sigma$         &  0.145 &  0.018 &   0.116 & 0.173 &   15490 &    1.0 \\
\midrule
\multicolumn{7}{c}{Transmission + Communication} \\
$\alpha_{1_\mu}$ &  0.052 &  0.042 &  -0.018 & 0.118 &   30904 &    1.0 \\
$\alpha_{2_\mu}$ &  0.297 &  0.102 &   0.138 & 0.469 &   56334 &    1.0 \\
$\alpha_{3_\mu}$ &  0.679 &  0.184 &   0.386 & 0.981 &   63206 &    1.0 \\
$\beta_{1_\mu}$  &  0.033 &  0.044 &  -0.040 & 0.102 &   18241 &    1.0 \\
$\beta_{2_\mu}$  &  0.093 &  0.073 &  -0.027 & 0.209 &   39754 &    1.0 \\
$\beta_{3_\mu}$  &  0.167 &  0.121 &  -0.033 & 0.359 &   53767 &    1.0 \\
$\sigma$         &  0.175 &  0.020 &   0.141 & 0.207 &   17902 &    1.0 \\
\midrule
\multicolumn{7}{c}{Difference} \\
$\Delta(\alpha_{1_\mu})$ & -0.047 &  0.079 &  -0.178 &    0.077 &   40911 &    1.0 \\
$\Delta(\alpha_{2_\mu})$ & -0.233 &  0.168 &  -0.504 &    0.040 &   55907 &    1.0 \\
$\Delta(\alpha_{3_\mu})$ & -0.434 &  0.241 &  -0.825 &   -0.037 &   57860 &    1.0 \\
$\Delta(\beta_{1_\mu})$  & -0.016 &  0.062 &  -0.118 &    0.084 &   23610 &    1.0 \\
$\Delta(\beta_{2_\mu})$  & -0.124 &  0.105 &  -0.295 &    0.047 &   35386 &    1.0 \\
$\Delta(\beta_{3_\mu})$  &  0.167 &  0.128 &  -0.045 &    0.371 &   50705 &    1.0 \\
$\Delta(σ)$              &  0.030 &  0.027 &  -0.014 &    0.074 &   16452 &    1.0 \\
\bottomrule
\end{tabular}
\label{exp2_parameter_estimates}
\end{threeparttable}
\end{center}
\end{table}
